To organize my acknowledgements, I will focus on the various pivot points throughout my graduate career and the people who helped me along my pathway.

I want to begin by thanking the three sources of support that helped me get over the finish line. This includes my immediate family, my friends in Ann Arbor, and my committee members. 
\begin{itemize}
    \item  First, I want to thank my family for being supportive both financially and emotionally throughout my entire graduate career. I would not have been able to achieve my current level of success without their help. 
    \item Next, I want to thank all of my friends both in Ann Arbor for cheering me on and providing me social outlets throughout my entire time in graduate school. I want to make a special shout-out to Jeffrey Willets, Brandon Romero, Ben Lempert, Erin Cikanek, Samuel Baltz, Eitan Paul, and Jeff Bilik for being instrumental in helping me craft my ideas throughout graduate school and for being an integral part of my inner social circle.
    \item Finally, I want to thank each member of my committee for taking the time to help me process my ideas and produce a dissertattion. 
    \begin{itemize}
        \item Thank you to \href{}{Frank Baumgartner} for showing me that graduate school in political science was even possible. If you had not (a) pass along my name to the Ralphe Bunche Summer Institute after the deadline had passed, (b) written me a letter of recommendation, and (c) convince the chair of the UNC department to write a letter of rec, I would not have 
    \end{itemize}
\end{itemize}
 

Next, I want to thank those who helped me transition from my undergraduate studies at UNC-Chapel Hill into my graduate program at the University of Michigan. 
\begin{itemize}
    \item Thank you to \href{}{John Aldrich}
    \item Thank you to \href{}{Susan Bickford}
\end{itemize}


While in graduate school, I was fortunate to have an array of mentors and teachers who helped me over the years.
\begin{itemize}
    \item Thank you to Kevin Quinn 
    \item Thank you to Pamela Brandwein, Mariah Zeisberg, and Robert Mickey for guiding me throughout my preliminary and early prospectus phase and for taking time out of their busy schedules to teach me new concepts. In addition, I want to thank the three of them for standing with me when I was sick during the summer of 2019. They pushed back against Rackham graduate school when it wanted me to dis-enroll and switch to medical leave (which would have caused me to lose my insurance) for failing to meet my second preliminary deadline. 
    
\end{itemize}
